\documentclass[a4paper,10pt]{article}
\usepackage[left=0.65in,right=0.65in,top=0.65in,bottom=0.65in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\setlist{noitemsep,topsep=2pt,parsep=1pt,partopsep=0pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.2ex plus 0.5ex minus .2ex}{0.8ex plus .1ex}

\begin{document}

\begin{center}
    {\huge \textbf{Okidi Norbert}} \\
    Mukono, Uganda \textbullet{} +256 771 032 224 \textbullet{} \href{mailto:oknorbert6@gmail.com}{oknorbert6@gmail.com} \textbullet{} \href{mailto:h4006554@gmail.com}{h4006554@gmail.com} \\
    GitHub: \href{https://github.com/okidi6}{okidi6} (Active) | \href{https://github.com/okidnorbert}{okidnorbert} (Archive) \textbullet{} \href{https://www.linkedin.com/in/okidi-norbert-881ba3305}{linkedin.com/in/okidi-norbert-881ba3305}
\end{center}

\section{Profile Summary}
Computer Science graduate from Uganda Christian University with a strong foundation in embedded systems, firmware development, and full-stack software development. Highly proficient in AI-driven engineering, actively leveraging advanced AI agents (Cursor, Antigravity, Claude, ChatGPT) across the entire software development lifecycle—from architecture and documentation to scripting, deep debugging, and deployment. Deeply passionate about blurring the lines between AI, hardware hacking, and offensive security. Also a competitive semi-professional basketball player, bringing discipline and strategic thinking to engineering challenges.

\section{Education}
\textbf{Uganda Christian University, Mukono} \hfill July 2026 \\
Bachelor of Science in Computer Science \hfill CGPA: 4.39/5.0
\begin{itemize}[leftmargin=*]
    \item \textbf{Key Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Database Programming, Web Programming, Cyber Security \& Digital Forensics, Data Science, Embedded Systems \& Microcontroller Programming, Robotics \& Control Systems, Very Large Scale Integration (VLSI), Digital Electronics \& Logic Design.
\end{itemize}

\textbf{Buddo Secondary School} --- Uganda Advanced Certificate of Education (UACE) \hfill 2022 \\
\textbf{St. Joseph's College Layibi} --- Uganda Certificate of Education (UCE) \hfill 2019

\section{Certifications}
\begin{itemize}[leftmargin=*]
    \item \textbf{Agent Master - Digital Agentic AI Hackathon} -- Founderz \& Microsoft
    \item \textbf{AI Skills Fest 2026} -- Microsoft
    \item \textbf{Cybersecurity Job Simulation} -- Commonwealth Bank
    \item \textbf{Digital Forensics \& Incident Response (DFIR)}
    \item \textbf{Cloud Foundations}
\end{itemize}

\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} C, C++, Python, Java, TypeScript, Bash, JavaScript, PHP
    \item \textbf{Embedded Systems \& Hardware:} Microcontrollers, Firmware Debugging, Raspberry Pi, Arduino, UART, Serial Communication, PLC Fundamentals, Industrial Automation
    \item \textbf{AI-Assisted Development:} Master of AI-driven engineering workflows (Cursor, Antigravity, Copilot, Lovable, Claude, ChatGPT) for rapid prototyping, complex debugging, and end-to-end SDLC automation.
    \item \textbf{AI \& Machine Learning:} PyTorch, TensorFlow, OpenCV, Scikit-learn, YOLO
    \item \textbf{Web \& Databases:} React, Next.js, Django, Flask, HTML/CSS, Tailwind CSS, PostgreSQL, MySQL, MongoDB, Supabase
    \item \textbf{DevOps \& Deployment:} Vercel, Hugging Face, AWS, Docker, Git, CI/CD Pipelines
    \item \textbf{Cybersecurity \& OS:} Linux (Kali, Debian, Ubuntu), Windows, Ethical Hacking, Penetration Testing, Digital Forensics
    \item \textbf{Creative Tools:} Adobe Photoshop, DaVinci Resolve, CapCut, Canva, Motion Graphics
\end{itemize}

\section{Professional Experience}
\textbf{Digital Transformation \& Growth Manager — Alora Initiative} \hfill Oct 2025 – Mar 2026
\begin{itemize}[leftmargin=*]
    \item Led digital transformation initiatives to drive growth and streamline organizational processes.
\end{itemize}

\textbf{IT Intern — Uganda Industrial Research Institute (UIRI)} \hfill May 2025 – July 2025
\begin{itemize}[leftmargin=*]
    \item Gained hands-on exposure to embedded systems and firmware development.
    \item Worked with PLC-based industrial automation systems and assisted in hardware-software integration.
    \item Developed and tested C/C++ hardware control programs and validation scripts.
    \item Participated in an exhibition showcasing a custom-built robotic arm project.
\end{itemize}

\textbf{Independent Technical Consultant \& Hardware Engineer} \hfill 2021 – Present
\begin{itemize}[leftmargin=*]
    \item Founded and operated a technical consultancy service resolving hardware and software issues for 150+ clients within the university community.
    \item Diagnosed low-level hardware faults, performed data recovery, configured operating systems (macOS, Linux, Windows), and executed component-level hardware upgrades.
    \item Automated system diagnostics and repetitive maintenance tasks using custom Python and Bash scripting.
    \item Configured local network devices, troubleshot routing issues, and performed deep-system software debugging.
\end{itemize}

\textbf{Independent Content Creator \& Video Editor} \hfill 2021 – Present
\begin{itemize}[leftmargin=*]
    \item Created and edited high-engagement short-form and long-form video content for social media platforms.
    \item Produced cinematic basketball edits, highlights, and promotional graphics with advanced transitions.
    \item Utilized AI-assisted editing workflows, sound synchronization, and digital storytelling techniques.
\end{itemize}

\section{Projects}
\textbf{BAKO-AI — Sports Analytics \& Computer Vision Platform} \hfill 2026
\begin{itemize}[leftmargin=*]
    \item Engineered an advanced real-time computer vision engine using PyTorch, OpenCV, and custom YOLO architectures for automated basketball tracking (player, ball, and court keypoints).
    \item Architected a 4-phase shot-form biometric skill diagnostics pipeline and a 7-module tactical analytics suite.
    \item Developed a robust full-stack system featuring automated video ingestion, Supabase/PostgreSQL database management, and interactive React/Next.js analytics dashboards.
\end{itemize}

\textbf{CineQuest — AI Movie Discovery Platform} \hfill 2025
\begin{itemize}[leftmargin=*]
    \item Spearheaded full-stack integration and recommendation model engineering for an interactive media search platform.
    \item Leveraged state-of-the-art AI agent workflows (Cursor, Antigravity) to accelerate API routing, CI/CD deployment, and high-performance scripting.
\end{itemize}

\textbf{Embedded Robotic Arm Control System} \hfill 2025
\begin{itemize}[leftmargin=*]
    \item Designed and fabricated a multi-degree-of-freedom (DOF) robotic arm prototype controlled via custom C/C++ firmware.
    \item Implemented low-level actuator control utilizing PWM-driven servo systems, UART serial protocols, and real-time sensor integration.
\end{itemize}

\section{Sports \& Extracurricular}
\textbf{UCU Canons – National Basketball League (NBL)} \hfill Shooting Guard, Small Forward, Power Forward
\begin{itemize}[leftmargin=*]
    \item Represented Uganda Christian University at the 2024 World University 3x3 Championship in Xiamen, China.
    \item Demonstrated high-level teamwork, leadership, and performance under pressure with 6+ years of competitive play.
\end{itemize}

\textbf{Other Interests:} 3D Design \& Printing (Designing STL files), Computer \& Electronics Repair, Cybersecurity Research.

\end{document}
