\documentclass[a4paper,10pt]{article}
\usepackage[left=0.55in,right=0.55in,top=0.45in,bottom=0.45in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\setlist{noitemsep,topsep=1pt,parsep=0.5pt,partopsep=0pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.6ex plus 0.2ex minus .1ex}{0.4ex plus .1ex}

\begin{document}

\begin{center}
    {\Huge \textbf{Okidi Norbert}} \\
    Mukono, Uganda \textbullet{} +256 771 032 224 \textbullet{} \href{mailto:oknorbert6@gmail.com}{oknorbert6@gmail.com} \textbullet{} \href{mailto:h4006554@gmail.com}{h4006554@gmail.com} \\
    GitHub: \href{https://github.com/okidi6}{okidi6} (Active) | \href{https://github.com/okidnorbert}{okidnorbert} (Archive) \textbullet{} \href{https://www.linkedin.com/in/okidi-norbert-881ba3305}{linkedin.com/in/okidi-norbert-881ba3305}
\end{center}

\vspace{-0.5em}

Computer Science graduate with strong expertise in embedded systems, full-stack development, and offensive security. Highly proficient in AI-driven software engineering, leveraging advanced AI assistants (Cursor, Antigravity, ChatGPT, Claude) across the entire SDLC—from architecture planning and documentation to scripting, debugging, and deployment—to drastically accelerate development cycles.

\section{Education}
\textbf{Uganda Christian University}, Mukono, Uganda \hfill July 2026 \\
Bachelor of Science in Computer Science \hfill CGPA: 4.39/5.0
\begin{itemize}[leftmargin=*]
    \item \textbf{Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Database Programming, Cyber Security \& Digital Forensics, Embedded Systems, Robotics \& Control Systems, Very Large Scale Integration (VLSI), Digital Electronics \& Logic Design.
\end{itemize}

\section{Technical Skills \& Certifications}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Languages:} C, C++, Python, Java, TypeScript, Bash, JavaScript, PHP
    \item \textbf{Embedded \& Hardware:} Microcontrollers, Firmware Debugging, Raspberry Pi, Arduino, UART, PLC Fundamentals
    \item \textbf{AI-Assisted Engineering:} Expert in leveraging Cursor, Antigravity, Copilot, Claude, and ChatGPT for rapid prototyping, architecture planning, automated debugging, and CI/CD troubleshooting.
    \item \textbf{AI \& ML Models:} PyTorch, TensorFlow, OpenCV, Scikit-learn, YOLO
    \item \textbf{Web \& Databases:} React, Next.js, Django, Flask, Tailwind CSS, PostgreSQL, MySQL, MongoDB, Supabase
    \item \textbf{DevOps \& OS:} Linux (Kali, Debian, Ubuntu), Vercel, Hugging Face, AWS, Docker, Git, CI/CD
    \item \textbf{Certifications:} Agent Master - Digital Agentic AI Hackathon (Founderz \& Microsoft), AI Skills Fest 2026 (Microsoft), Cybersecurity Job Simulation (Commonwealth Bank), Digital Forensics \& Incident Response (DFIR), Cloud Foundations
\end{itemize}

\section{Professional Experience}
\textbf{Digital Transformation \& Growth Manager — Alora Initiative} \hfill Oct 2025 – Mar 2026
\begin{itemize}[leftmargin=*, noitemsep]
    \item Led digital transformation initiatives to drive growth and streamline organizational processes.
\end{itemize}

\textbf{IT Intern — Uganda Industrial Research Institute (UIRI)} \hfill May 2025 – July 2025
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed and tested C/C++ hardware control programs for PLC-based industrial automation systems.
    \item Assisted in end-to-end hardware-software integration, system debugging, and remote testing.
    \item Participated in the technical demonstration and exhibition of a custom-built robotic arm.
\end{itemize}

\textbf{Independent Technical Consultant \& Hardware Engineer} \hfill 2021 – Present
\begin{itemize}[leftmargin=*, noitemsep]
    \item Founded and operated a technical consultancy service resolving hardware and software issues for 150+ clients within the university community.
    \item Diagnosed low-level hardware faults, performed data recovery, configured operating systems (macOS, Linux, Windows), and executed component-level hardware upgrades.
\end{itemize}

\section{Projects}
\textbf{BAKO-AI — Sports Analytics \& CV Platform}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Engineered an advanced real-time computer vision engine using PyTorch, OpenCV, and custom YOLO architectures for player, ball, and court keypoint tracking.
    \item Architected a 4-phase biometric shot diagnostics pipeline and a 7-module tactical analytics suite.
\end{itemize}

\textbf{CineQuest — AI Movie Discovery Platform}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Spearheaded full-stack integration and recommendation model engineering for an interactive media search platform.
    \item Leveraged state-of-the-art AI agent workflows (Cursor, Antigravity) to accelerate API routing and CI/CD deployment.
\end{itemize}

\textbf{Embedded Robotic Arm Control System}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and fabricated a multi-degree-of-freedom robotic arm prototype controlled via custom C/C++ firmware.
    \item Implemented low-level actuator control utilizing PWM-driven servo systems, UART serial protocols, and real-time sensor integration.
\end{itemize}

\section{Sports \& Leadership}
\textbf{UCU Canons – National Basketball League (NBL)} \hfill Shooting Guard, Small Forward, Power Forward
\begin{itemize}[leftmargin=*, noitemsep]
    \item Represented Uganda Christian University at the 2024 World University 3x3 Championship in Xiamen, China.
    \item Demonstrated high-level teamwork, leadership, and performance under pressure with 6+ years of competitive play.
\end{itemize}

\end{document}
